---
title: "02_stats"
author: "Jessica Kowalski, University of British Columbia, jkowals@zoology.ubc.ca"
date: "2024-12-12"
output: html_document
---
Last updated: September 

This Markdown document contains the required code for all analyses in "The deterministic underpinnings of demographic stochasticity". 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup
**run before loading packages to avoid errors**
import data from cleaning script
```{r, echo = FALSE, message = FALSE}
#source from Rmarkdown
source_rmd <- function(file, local = FALSE, ...){
  options(knitr.duplicate.label = 'allow')

  tempR <- tempfile(tmpdir = ".", fileext = ".R")
  on.exit(unlink(tempR))
  knitr::purl(file, output=tempR, quiet = TRUE)

  envir <- globalenv()
  source(tempR, local = envir, ...)
}
source_rmd('01_data_clean.Rmd')
```
'source_rmd' pulls code chunks directly from Rmarkdown documents and avoids the verbage (like 'source' for Rmd docs).

load packages
```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(emmeans) #v. 2.0.4
library(car) #v. 3.1-5
library(glmmTMB) #v. 1.1.14
library(DHARMa) #v. 0.4.7
library(ggeffects) #v. 2.3.2
library(correlation) #v. 0.8.8
#library(mgcv) #v. 1.9-3
#library(ggpubr) #v. 0.6.1
#library(gratia) #v. 0.10.0
#library(ggExtra)
#library(MuMIn)
library(splines) #v. 4.5.2
#library(boot)
#library(performance)
```

# Q1 Does the timing of a stressor (i.e. drought) impact the variance in seed output? 

## model selection

```{r}
#fit model where dispersion = constant (null hypothesis = no difference in dispersion amongst groups)
seed.var_pois <- glmmTMB(matSeeds ~ drought, family = poisson(), REML = TRUE, data = demo_fecund) #mean = variance
seed.var_nbinom <- glmmTMB(matSeeds ~ drought, family = nbinom1(), REML = TRUE, data = demo_fecund) #variances increases linearly with mean 
seed.var_nbinom2 <- glmmTMB(matSeeds ~ drought, family = nbinom2(), REML = TRUE, data = demo_fecund) #variance increases exponentially with mean
seed.var_log <- glmmTMB(matSeeds +1 ~ drought, family = gaussian(link = "log"), REML = TRUE, data = demo_fecund) #variance is average distance between sample value and mean
seed.var_compois <- glmmTMB(matSeeds ~ drought, family = compois(), REML = TRUE, data = demo_fecund) #model is so flexible, no real way to characterize variance-mean relationship, but models over & underdispersed count data by generalizing the poisson distribution

#fit model where dispersion is treatment-specific 
seed.var_disp <- glmmTMB(matSeeds ~ drought, dispformula = ~drought, family = poisson(), REML = TRUE, data = demo_fecund)
seed.var_dispnbinom <- glmmTMB(matSeeds ~ drought, dispformula = ~drought, family = nbinom1(), REML = TRUE, data = demo_fecund)
seed.var_dispnbinom2 <- glmmTMB(matSeeds ~ drought, dispformula = ~drought, family = nbinom2(), REML = TRUE, data = demo_fecund)
seed.var_displog <- glmmTMB(matSeeds +1 ~ drought, dispformula = ~drought, family = gaussian(link = "log"), REML = TRUE, data = demo_fecund)
seed.var_dispcompois <- glmmTMB(matSeeds ~ drought, dispformula = ~drought, family = compois(), REML = TRUE, data = demo_fecund)

#check fit
poiss_output <- simulateResiduals(seed.var_pois)
plot(poiss_output)
testDispersion(seed.var_pois)
#so so so incredibly bad
poiss_output2 <- simulateResiduals(seed.var_disp)
plot(poiss_output2)

nbinom_output <- simulateResiduals(seed.var_nbinom)
plot(nbinom_output)
testDispersion(seed.var_nbinom)
#underdispersed & bad KS test & heteroskedasticity
nbinom_output2 <- simulateResiduals(seed.var_dispnbinom)
plot(nbinom_output2)

nbinom2_output <- simulateResiduals(seed.var_nbinom2)
plot(nbinom2_output)
#underdispersed & bad KS test & heteroskedasticity
nbinom2_output2 <- simulateResiduals(seed.var_dispnbinom2)
plot(nbinom2_output2)

compois_output <- simulateResiduals(seed.var_compois, n = 1000)
plot(compois_output)
testCategorical(compois_output, demo_fecund$drought)

compois_output2 <- simulateResiduals(seed.var_dispcompois, n = 1000)
plot(compois_output2)
testCategorical(compois_output2, demo_fecund$drought)

log_output <- simulateResiduals(seed.var_log)
plot(log_output)

log_output2 <- simulateResiduals(seed.var_displog)
plot(log_output2)

anova(seed.var_disp, seed.var_dispnbinom, seed.var_dispnbinom2, seed.var_dispcompois)
# poisson, nbinom1 & nbinom2 models have fit issues (dispersion, residual structure)
# log-gaussian fits well but data was generated by a count process so conway-maxwell is best choice 

#compare models using likelihood ratio test to test for difference in variance amongst drought treatments (disp model better fit = variance differs amongst drought treatments)
anova(seed.var_compois, seed.var_dispcompois)

#what is the difference in mean seed set amongst drought treatments? 
Anova(seed.var_dispcompois, type = 2) #p < 0.001
emmeans(seed.var_dispcompois, pairwise ~ drought)

matSeeds_predict <- as.data.frame(ggemmeans(seed.var_dispcompois, terms = c("drought"))) %>% 
  rename(drought = x,
         matSeeds = predicted)
#save for plotting
#write.csv(matSeeds_predict, file = "data_clean/matSeeds_predict.csv")
```

## planned paired contrast model comparisons

Ran into problems using Wald's approximation (can happen with non-normally distributed data & B. Bolker said model comparison approach is more reliable) so can't rely on model outputs on the dispersion component calculated using confint() or Anova(component = "disp"). Decided to run paired contrasts for post-hoc analysis using the same model comparison procedure above: d1 (early) vs d0 (control) and d3 (late) vs d0 (control) 

contrast 1: control (d0) vs early drought (d1)
```{r}
# compute raw log means for starting values
mean_seeds <- tapply(demo_fecund$matSeeds, demo_fecund$drought, mean, na.rm = TRUE)

start_list <- list(
beta = c(
log1p(mean_seeds["d0"]), # intercept
log1p(mean_seeds["d1"]) - log1p(mean_seeds["d0"])# drought effect
))

seed.var_pair1 <- glmmTMB(matSeeds ~ drought, 
                          family = compois(link = "log"), 
                          REML = TRUE, start = start_list,
                          data = subset(demo_fecund, 
                                        drought =="d0"|drought == "d1"))

seed.var_pair1.disp <- update(seed.var_pair1, dispformula = ~ drought)

plot(simulateResiduals(seed.var_pair1))
plot(simulateResiduals(seed.var_pair1.disp))

anova(seed.var_pair1, seed.var_pair1.disp) # no difference
```

contrast 2: control (d0) vs late drought (d3)
```{r}
# compute raw log means for starting values
start_list2 <- list(
beta = c(
log1p(mean_seeds["d0"]), # intercept
log1p(mean_seeds["d3"]) - log1p(mean_seeds["d0"]) # drought effect
))

seed.var_pair2 <- glmmTMB(matSeeds ~ drought,
                          family = compois(link="log"),
                          REML = TRUE, start = start_list2,
                          data = subset(demo_fecund, drought=="d0"|drought=="d3"))

seed.var_pair2.disp <- update(seed.var_pair2, dispformula = ~ drought)

plot(simulateResiduals(seed.var_pair2, n = 1000))
plot(simulateResiduals(seed.var_pair2.disp, n = 1000))

anova(seed.var_pair2, seed.var_pair2.disp) 
```

### parametric bootstrap to calculate confidence intervals 

Ran into problems w/ Wald's approximation (basis of calculating confidence intervals for model parameters in glmmTMB), so using parametric bootstrapping method to estimate confidence intervals for dispersion parameters associated with each drought treatment
```{r}
d0Disp_parm <- NA_real_
d1Disp_parm <- NA_real_
d3Disp_parm <- NA_real_

set.seed(123)
for(i in 1:1000) {
  
  data <- model.frame(seed.var_dispcompois)
  data$sim[as.numeric(rownames(model.frame(seed.var_dispcompois)))] <- simulate(seed.var_dispcompois)[[1]]
  
  log_means <- log(tapply(data$sim, data$drought, mean, na.rm = TRUE))

  start_list <- list(
    beta = c(
      log_means["d0"],
      log_means["d1"] - log_means["d0"],
      log_means["d3"] - log_means["d0"]
    )
  )
  
#run model
  lm_sim <- glmmTMB(sim ~ drought, 
                    dispformula = ~drought, 
                    family = compois(link = "log"), 
                    start = start_list,
                    na.action = "na.fail",
                    REML = TRUE, 
                    data = data)

#extract & compute dispersion parameters
   temp_disp <- fixef(lm_sim)$disp
  
d0Disp_parm[i] <-exp(as.numeric(temp_disp["(Intercept)"]))
d1Disp_parm[i] <- exp(as.numeric(temp_disp["(Intercept)"]) + as.numeric(temp_disp["droughtd1"]))
d3Disp_parm[i] <- exp(as.numeric(temp_disp["(Intercept)"]) + as.numeric(temp_disp["droughtd3"]))
  
}
```

```{r}
#save observed dispersion parameters from original data
disp.coef <- fixef(seed.var_dispcompois)$disp

#calculate dispersion parameter
obs_d0 <- exp(as.numeric(disp.coef["(Intercept)"])) #estimate = 1/v
obs_d1 <-  exp(as.numeric(disp.coef["(Intercept)"]) + as.numeric(disp.coef["droughtd1"])) #estimates of d1 and d3 calculated using d0 as dummy variable (verifiable using 'predict(seed.var_dispcompois, type = "disp")')
obs_d3 <- exp(as.numeric(disp.coef["(Intercept)"]) + as.numeric(disp.coef["droughtd3"]))

#calculate percentile 95% CIs from parameteric bootstrap
alpha <- 0.05

parm_boot_disp_perc <- tibble(
  drought = c("d0", "d1", "d3"), 
  dispcoeff = c(obs_d0, obs_d1, obs_d3),
  upperci = c(as.numeric(quantile(d0Disp_parm, c(1-alpha/2))), 
              as.numeric(quantile(d1Disp_parm, c(1-alpha/2))),
              as.numeric(quantile(d3Disp_parm, c(1-alpha/2)))),
  lowerci = c(as.numeric(quantile(d0Disp_parm, c(alpha/2))), 
              as.numeric(quantile(d1Disp_parm, c(alpha/2))),
              as.numeric(quantile(d3Disp_parm, c(alpha/2))))
)

#save for plotting
#write.csv(parm_boot_disp_perc, file = "data_clean/disp_CI.csv")
```

# Q2 Does early life condition affect individual response to stress (aka drought) following the Matthew effect or compensatory growth dynamics? 

note: all analyses using data from the ontogeny experiment is only using data collected from day 1-135 before **any** irrigation issues occurred 

## Does germination treatment matter? 

Looking at whether mean height before and after drought differ between two germination treatments to assess if can collapse germination treatments together 
```{r}
germ_grow <- grow_time %>% 
  filter(population == "p6" & drought == "d0" & expDayHeight == 135 |
           population == "p6" & drought == "d1" & expDayHeight == 135) 
  

germ_height_lm <- glmmTMB(height.Cm ~ drought * germination,
                          data = germ_grow)

germ_height_output <- simulateResiduals(germ_height_lm); plot(germ_height_output)

Anova(germ_height_lm, type = 3)

germ_height <- ggemmeans(germ_height_lm, terms = c("germination", "drought"))
plot(germ_height)

pred_germ <- as.data.frame(germ_height) %>% 
  rename(germination = x,
         drought = group,
         height.Cm = predicted) 

#save for plotting
#write.csv(pred_germ, file = "data_clean/pred_germ.csv")
```

## Does the Matthew effect shape individual response to acute stress? 

According to Matthew effect, past condition predicts future condition, so we expect a positive correlation between height prior to drought onset and height after drought onset to be maintained over extent of study period 

if correlation goes away (null association), then everyone is performing similarly, regardless of how they started
if correlation becomes negative, then weaker pre-drought get stronger post-drought 

```{r}
# extract pre-drought height for each replicate
predrought_height <- grow_time %>% 
  filter(population == "p6" & drought == "d0" & expDayHeight <= 135 | # cutting off @ day 135 b/c before irrigation problems
           population == "p6" & drought == "d1" & expDayHeight <=135) %>%
  group_by(cellID) %>% 
  reframe(
    preDrought.Cm = case_when(expDayHeight == 16 ~ height.Cm,
                                 TRUE ~ NA)
  ) %>% 
  drop_na(preDrought.Cm)

# make data frame for remaining calculations
grow_p6 <- grow_time %>% 
  filter(population == "p6" & drought == "d0" & expDayHeight <= 135 | # remove other populations and only keep d1 and d0
           population == "p6" & drought == "d1" & expDayHeight <= 135) %>%
  dplyr::select(cellID, drought, height.Cm, expDayHeight, germination) %>% 
  left_join(predrought_height, by = "cellID") %>% 
  #pivot_wider(values_from = "height.Cm", names_from = "expDayHeight") %>% 
  dplyr::select(-cellID) %>% 
  mutate(
    expDayHeight = factor(expDayHeight),
  ) %>% 
  relocate(c(drought, expDayHeight))
```


calculate correlation coefficients within each drought group
```{r}
#d0 height correlations
d0_correlations <- grow_time %>% 
  filter(population == "p6" & drought == "d0" & expDayHeight <= 135) %>%
  dplyr::select(cellID, drought, height.Cm, expDayHeight) %>% 
  left_join(predrought_height, by = "cellID") %>% 
  #pivot_wider(values_from = "height.Cm", names_from = "expDayHeight") %>% 
  dplyr::select(-cellID, - drought) %>% 
  mutate(
    expDayHeight = factor(expDayHeight)
  ) %>% 
  group_by(expDayHeight) %>% 
  correlation() %>% 
  as.data.frame() %>% 
  mutate(
    drought = c("d0")
  ) %>% 
  relocate(drought)

#d1 height correlations
d1_correlations <- grow_time %>% 
  filter(population == "p6" & drought == "d1" & expDayHeight <= 135) %>%
  dplyr::select(cellID, drought, height.Cm, expDayHeight) %>% 
  left_join(predrought_height, by = "cellID") %>% 
  #pivot_wider(values_from = "height.Cm", names_from = "expDayHeight") %>% 
  dplyr::select(-cellID, - drought) %>% 
  mutate(
    expDayHeight = factor(expDayHeight)
  ) %>% 
  group_by(expDayHeight) %>% 
  correlation() %>% 
  as.data.frame() %>% 
  mutate(
    drought = c("d1")
  ) %>% 
  relocate(drought)
```

make data frame for correlation model 
```{r}
raw_corr <- bind_rows(d0_correlations, d1_correlations) %>% 
  dplyr::select(drought, Group, r, CI_low, CI_high, p) %>% 
  mutate(
    expDayHeight = as.numeric(Group),
    drought = factor(drought, levels = c("d0", "d1")),
    corrected_r = case_when(p > 0.05 ~ 0,
                            TRUE ~ r
      
    )
  ) %>% 
  filter(expDayHeight > 9) # remove first day b/c day 16 = pre-drought height measurement

#save for plotting
#write.csv(raw_corr, file = "data_clean/raw_corr.csv")
```

correlation model to test the Matthew effect
```{r}
# run linear model to check if slopes differ 

corr_lmr2 <- glmmTMB(r ~ drought * ns(expDayHeight, df = 2), # use model based on raw data
                   data = raw_corr)

corr_output <- simulateResiduals(corr_lmr2); plot(corr_output) 

#using splines instead of higher order polynomials b/c polynomials are too restrictive & can allow single point in one part of curve to greatly influence other parts of curve (https://hbiostat.org/rmsc/)

corr_lm <- corr_lmr2

Anova(corr_lm, type = '3') # interaction 

fixef(corr_lm)

emtrends(corr_lm, pairwise ~ drought, var = 'expDayHeight', type = "response", max.degree = 2)

corr_heights <- ggemmeans(corr_lm, terms = c("expDayHeight [all]", "drought"))
plot(corr_heights)

pred_corr_heights <- as.data.frame(corr_heights) %>% 
  rename(expDayHeight = x,
         drought = group,
         r = predicted) 

#save for plotting
#write.csv(pred_corr_heights, file = "data_clean/pred_corr_heights.csv")
```

## How does variance in height change over the course of the ontogeny experiment? Are replicates becoming more or less similar in height over time? 

```{r}
# run linear model to estimate dispersion for each experiment day * drought group combo 
raw_height_lm <- grow_p6 %>% 
  filter(expDayHeight != "9") # remove first day b/c day 16 = pre-drought height measurement

raw_height_lm %>% 
  ggplot(aes(x = log(height.Cm))) +
  geom_histogram() +
  theme_classic() +
  facet_wrap(~ expDayHeight)

height_lm <- glmmTMB(log(height.Cm) ~ drought * expDayHeight, #experiment day as factor to look at dispersion
                  family = gaussian(link = "identity"),
                  data = raw_height_lm)

height_disp_lm <- glmmTMB(log(height.Cm) ~ drought * expDayHeight, #experiment day as factor to look at dispersion
                  dispformula = ~ drought * expDayHeight,
                  family = gaussian(link = "identity"),
                  data = raw_height_lm)

h_output <- simulateResiduals(height_lm, n = 1000); plot(h_output)
hdisp_output <- simulateResiduals(height_disp_lm, n = 1000); plot(hdisp_output)

anova(height_lm, height_disp_lm) # dispersion model better fit
```

```{r}
#extract dispersion estimates & associated confidence intervals from model
hdisp_vec <- fixef(height_disp_lm)$disp
#put alpha estimates into a df 
hdisp_coefs <- tibble(
  term = names(hdisp_vec),
  Estimate = as.numeric(hdisp_vec)
) %>% 
  mutate(
    term = case_when(term == "(Intercept)" ~ "d0-16",
                     term == "expDayHeight23" ~ "d0-23",
                     term == "expDayHeight30" ~ "d0-30",
                     term == "expDayHeight37" ~ "d0-37",
                     term == "expDayHeight44" ~ "d0-44",
                     term == "expDayHeight51" ~ "d0-51",
                     term == "expDayHeight58" ~ "d0-58",
                     term == "expDayHeight65" ~ "d0-65",
                     term == "expDayHeight72" ~ "d0-72",
                     term == "expDayHeight79" ~ "d0-79",
                     term == "expDayHeight92" ~ "d0-92",
                     term == "expDayHeight107" ~ "d0-107",
                     term == "expDayHeight114" ~ "d0-114",
                     term == "expDayHeight121" ~ "d0-121",
                     term == "expDayHeight128" ~ "d0-128",
                     term == "expDayHeight135" ~ "d0-135",
                     term == "droughtd1" ~ "d1-16",
                     term == "droughtd1:expDayHeight23" ~ "d1-23",
                     term == "droughtd1:expDayHeight30" ~ "d1-30",
                     term == "droughtd1:expDayHeight37" ~ "d1-37",
                     term == "droughtd1:expDayHeight44" ~ "d1-44",
                     term == "droughtd1:expDayHeight51" ~ "d1-51",
                     term == "droughtd1:expDayHeight58" ~ "d1-58",
                     term == "droughtd1:expDayHeight65" ~ "d1-65",
                     term == "droughtd1:expDayHeight72" ~ "d1-72",
                     term == "droughtd1:expDayHeight79" ~ "d1-79",
                     term == "droughtd1:expDayHeight92" ~ "d1-92",
                     term == "droughtd1:expDayHeight107" ~ "d1-107",
                     term == "droughtd1:expDayHeight114" ~ "d1-114",
                     term == "droughtd1:expDayHeight121" ~ "d1-121",
                     term == "droughtd1:expDayHeight128" ~ "d1-128",
                     term == "droughtd1:expDayHeight135" ~ "d1-135",
                     TRUE ~ "NA")
  ) %>% 
  separate(term, c("drought", "expDayHeight"), sep = "-") 

hdisp_confint <- as_tibble(confint(height_disp_lm, parm = "sigma", method = "profile"), rownames = "term") %>% 
  mutate(
    term = case_when(term == "disp~(Intercept)" ~ "d0-16",
                     term == "disp~expDayHeight23" ~ "d0-23",
                     term == "disp~expDayHeight30" ~ "d0-30",
                     term == "disp~expDayHeight37" ~ "d0-37",
                     term == "disp~expDayHeight44" ~ "d0-44",
                     term == "disp~expDayHeight51" ~ "d0-51",
                     term == "disp~expDayHeight58" ~ "d0-58",
                     term == "disp~expDayHeight65" ~ "d0-65",
                     term == "disp~expDayHeight72" ~ "d0-72",
                     term == "disp~expDayHeight79" ~ "d0-79",
                     term == "disp~expDayHeight92" ~ "d0-92",
                     term == "disp~expDayHeight107" ~ "d0-107",
                     term == "disp~expDayHeight114" ~ "d0-114",
                     term == "disp~expDayHeight121" ~ "d0-121",
                     term == "disp~expDayHeight128" ~ "d0-128",
                     term == "disp~expDayHeight135" ~ "d0-135",
                     term == "disp~droughtd1" ~ "d1-16",
                     term == "disp~droughtd1:expDayHeight23" ~ "d1-23",
                     term == "disp~droughtd1:expDayHeight30" ~ "d1-30",
                     term == "disp~droughtd1:expDayHeight37" ~ "d1-37",
                     term == "disp~droughtd1:expDayHeight44" ~ "d1-44",
                     term == "disp~droughtd1:expDayHeight51" ~ "d1-51",
                     term == "disp~droughtd1:expDayHeight58" ~ "d1-58",
                     term == "disp~droughtd1:expDayHeight65" ~ "d1-65",
                     term == "disp~droughtd1:expDayHeight72" ~ "d1-72",
                     term == "disp~droughtd1:expDayHeight79" ~ "d1-79",
                     term == "disp~droughtd1:expDayHeight92" ~ "d1-92",
                     term == "disp~droughtd1:expDayHeight107" ~ "d1-107",
                     term == "disp~droughtd1:expDayHeight114" ~ "d1-114",
                     term == "disp~droughtd1:expDayHeight121" ~ "d1-121",
                     term == "disp~droughtd1:expDayHeight128" ~ "d1-128",
                     term == "disp~droughtd1:expDayHeight135" ~ "d1-135",
                     TRUE ~ "NA")
  ) %>% 
  separate(term, c("drought", "expDayHeight"), sep = "-")
```

```{r}
# in glmmTMB, sigma returns the maximum likelihood estimate of the standard deviation for the gaussian distribution
# used log(height) in model so need to exponentiate to get back into response scale 

# d0-16 = reference value
coef_ref <- hdisp_coefs$Estimate[1]

# make a new column for residual standard error
hdisp_coefs$sd <- NA

# loop to add each Estimate to the reference value
for (i in 1:nrow(hdisp_coefs)) {
  if (i == 1) {
    #use reference value for first entry
    hdisp_coefs$sd[i] <- exp(coef_ref)
  } else {
    #for all other entries, add estimate to reference value
    hdisp_coefs$sd[i] <- exp(coef_ref + hdisp_coefs$Estimate[i])
  } 
}

#calculate upper & lower CI bounds

# d0-16 = reference values for upper and lower bounds
ci_up_ref <- hdisp_confint$`97.5 %`[1]
ci_low_ref <- hdisp_confint$`2.5 %`[1]

# make new columns for upper & lower confidence intervals
hdisp_confint$upperCI <- NA
hdisp_confint$lowerCI <- NA

# loop to add each upper/lower boundary to the reference value
for (i in 1:nrow(hdisp_confint)) {
  if (i == 1) {
    #use reference values for first entry
    hdisp_confint$upperCI[i] <- exp(ci_up_ref)
    hdisp_confint$lowerCI[i] <- exp(ci_low_ref)
  } else {
    #for all other entries, add estimate to reference value
    hdisp_confint$upperCI[i] <- exp(ci_up_ref + hdisp_confint$`97.5 %`[i])
    hdisp_confint$lowerCI[i] <- exp(ci_low_ref + hdisp_confint$`2.5 %`[i])
  } 
}

#extract drought group mean heights on each experiment day
hfixed_coeff <- as_tibble(ggemmeans(height_disp_lm, c("drought", "expDayHeight"), type = "fixed"))  %>% 
  rename(drought = x, 
         expDayHeight = group) %>% 
  dplyr::select(drought, expDayHeight, predicted)

#dispersion table 
height_disp_coef <- hdisp_coefs %>% 
  left_join(hdisp_confint, by = c("drought", "expDayHeight")) %>% 
  left_join(hfixed_coeff, by = c("drought", "expDayHeight")) %>% 
  rename(mean = predicted, 
         upperSD = upperCI, 
         lowerSD = lowerCI) %>% 
  mutate(
    variance = sd^2, 
    upperVar = upperSD^2,
    lowerVar = lowerSD^2,
    expDayHeight = factor(expDayHeight, 
                          levels = c("16", "23", "30", "37", "44", "51", "58", "65", "72", "79", 
                                     "92", "107", "114", "121", "128", "135"))
  ) %>% 
  dplyr::select(-Estimate, -`97.5 %`, -`2.5 %`)

#save for plotting
#write.csv(height_disp_coef, file = "data_clean/height_disp_coef.csv")
```